### 2013-11-25 PositionPaper/incremental.tex
Incremental.tex more stable as time goes by ...

%-----------------------------------------------------------------
\subsection{Computing query SLA}
\label{sec:slaModel}
%-----------------------------------------------------------------

@@

The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs. Higher level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source. The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user. One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

To meet this objective, we assume that services export SLA's (i.e., agreed SLA's) that are sometimes of finer granularity than those defined by the user.  The service SLA measures are are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called. For example the cost, which includes the price of calling the service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network. With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.

The challenge  is  to determine whether their joint use is compatible with the individual SLA. We propose a classification of SLA measures represents the relationship between fine grained measures used by agree SLAs and coarse grained measures used in globel SLAs. It specifies also how to compute coarse grained measures with fine grained ones. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.

@@

%-----------------------------------------------------------------
\subsection{Monitoring the resources consumed by the evaluation process}
\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
% Indeed, let consider a request R launched by a user who specifies a %number of constraints on the environment execution.

@@

 We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results. Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data). For two different queries, they will be negotiated in the same way. These previously negotiated SLAs are reusable.

In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ... ).
%Given this proposal, we identify several issues:
%- Level modeling would require a model that allows the representation of SLA integration.
%- There should also be a template for representing the requirements expressed by the user
%- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request. This implies mapping between property and expressed clauses being.

Monitor the consumption of resources, the execution, time, behaviour of the services and make decisions

>>>>

%-----------------------------------------------------------------
\subsection{Deriving a query SLA}
\label{sec:slaModel}
%-----------------------------------------------------------------

@@

The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs that leads to a {\em derived SLA} that guides the evaluation of a query. A query has associated preferences  expressed as macroscopic constraints: execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode. These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assined storage space, number of requests, transfered Mega Octets, etc.). Given a query and its preferences statement, the system  finds relevant service compositions that produces results  such that when combined, they meet the required constraints.

%One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.

We assume that services export SLA's (i.e., agreed SLA's) that define measures  of finer granularity than those defined by the user.  The service SLA measures  are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request. These measures are in general computed by monitoring the execution and conversations associted to services. For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service. This request  includes the price of calling a service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network. Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
 Measures can be also hybrid, in the sense that they can be statically stated partially but they require to be precised at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

Given agreed SLA's and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.  The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.

 We propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA is can be seen as a set of equations that has to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

@@

%-----------------------------------------------------------------
\subsection{Dealing with the resources consumed by the evaluation process}
\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
% Indeed, let consider a request R launched by a user who specifies a %number of constraints on the environment execution.

@@

 Our data provision and integration approach relys on data services deployed on one or different providers and it is delivered as a DaaS. This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process. It is thus important to optimize the use of these resources.

 We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.  Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service). Instead of recomputing the derived SLA every time, we propose to store it and reuse it for other queries.

Second, precalculated queries and partial results can be also stored in cache or in a persistent supprt. Rewritting and optimization results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Being able of storing such SLAs will depend on the cloud subscription (data access, intermediate storage capacity , cost of storage , etc ... ).
%Given this proposal, we identify several issues:
%- Level modeling would require a model that allows the representation of SLA integration.
%- There should also be a template for representing the requirements expressed by the user
%- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request. This implies mapping between property and expressed clauses being.

As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time. In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transfered when services deliver results. These computations are used dynamically for instanciating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query. Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.
